Comparing R packages for calculation of persistent homology

### 2020-03-08 tdabench-paper/tdabench.Rmd
revised text

\subsection{Comparison of alpha and Vietoris-Rips complexes within GUDHI}
The GUDHI library provided functionality to calculate persistent homology with Rips and Alpha complexes. 
Therefore, we only used the GUDHI library to compare performance between Rips and Alpha complexes.

@@

\section{Acknowledgements}
Emily Dolson, PhD for assistance in using the HPC for collecting data

>>>>

\subsection{Comparison of alpha and Vietoris-Rips complexes within GUDHI}
<!--SHOULD BE IN METHODS
The GUDHI library provided functionality to calculate persistent homology with Rips and Alpha complexes. 
Therefore, we only used the GUDHI library to compare performance between Rips and Alpha complexes.-->

@@

\section{Acknowledgements}
Emily Dolson, PhD for assistance with using a high-performance computing node for data collection.
